---
title: "Rmarkdown Lab Homework"
author: "Evan Rank"
date: "3/3/2021"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      fig.path = "../output/")
```

# **Load Packages**
I will continue to use the Penguins data to demonstrate tables and figures in Markdown.

```{r}
library(here)
library(tidyverse)
library(palmerpenguins)
```

# **Clean Penguins Data**  

```{r}
PenguinsClean <- penguins %>%
  filter(complete.cases(.))
```

# **Summarize**  

Let's look at the means of the body mass variable that we will quantify in our graph.

```{r}
PenguinsMean <- PenguinsClean %>%
  group_by(sex, species) %>%
  summarise(mean_body_mass =mean(body_mass_g)) %>% 
  write_csv(here("Week_6","output", "meanmass.csv"))

  view(PenguinsMean)
```

# **Table**

I will start by looking at the mean body mass of our penguin species by sex.

|*Sex* |*Species* |*Mean Body Mass*|
|:-----|:----------|:-------|
|female|	Adelie	 |3368.836|
|female|	Chinstrap|3527.206|
|female|	Gentoo	 |4679.741|
|male  |	Adelie	 |4043.493|
|male  |	Chinstrap|3938.971|
|male  |	Gentoo	 |5484.836|

# **Figure**

We are going to plot the distribution of body mass by *species* and *sex*. 
```{r Penguin Figure HW}
PenguinFigureHW<-PenguinsClean %>% 
  ggplot(aes(x=species, y=body_mass_g, color=sex))+
    geom_boxplot()+
  labs(title = "Penguin Body Mass by Species and Sex",
       x= "Species",
       y= "Body Mass (g)",
       color="Sex")
PenguinFigureHW #need to recall the object to display the graph in rmarkdown
```

