---
title: "Functions Lab"
author: "Evan Rank"
date: "3/24/2021"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      fig.path = "../output/")
```

## Introduction

  We will be practicing with the Palmer Penguins data to create one function for box plotting and another for defining a ratio between any two data points.
  
## Load Libraries

```{r}
library(tidyverse)
library(here)
library(palmerpenguins) #our data
```

## First Function (Data Frame)

```{r}
measurement_ratio <- function(x,y){ #simple function to return division
  ratio <- (x /y)
  return(ratio)
}
```

## Testing Data Function

```{r}
penguinsratio <- penguins %>% 
  mutate(length_depth_ratio = measurement_ratio(bill_length_mm, bill_depth_mm)) #first example

penguinsratio <-penguinsratio %>% #updating the same object
  mutate(flipper_bodymass_ratio = measurement_ratio(flipper_length_mm, body_mass_g)) #second example

head(penguinsratio)
```

## Second Function (Plot)
  
  I am going to make a box plot function, so I can apply it quickly to any data if I want to view the distribution.

```{r, penguinFlipper}
penguins %>% 
  ggplot(aes(x=species, y=flipper_length_mm, color=island))+ #Plot used as the base of the function
  geom_boxplot() 
```

## Copy and Replace to Create Function

```{r}
fplot <- function (data, x, y, z){ #replacing defined variables with x, y, or group)
    ggplot(data, aes(x={{x}}, y={{y}}, color={{z}}))+
   geom_boxplot()
}
```

## Testing Function

```{r, fpenguinFlipper}
fplot(data = penguins, x=species, y=flipper_length_mm, z=island)
```

## New Example with Layering

```{r, fpenguinBodyMass}
fplot(data = penguins, x=species, y=body_mass_g, z=species)+ #Testing with body mass, color by species for simpler viewing
  facet_wrap(~island)+ #why we previously colored by species instead of island
  labs(x="Species", #adding labels as well
       y="Body Mass (g)",
       color= "Island",
       title="Body Mass of Penguins by Species")
  
```

