---
title: "Good plot / Bad plot"
author: "Evan Rank"
date: "3/10/2021"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      fig.path = "../output/")
```

## Introduction

My goal is to present a single dataset twice, one to make an example of how *not* to do a plot and the other as an example of how a publication-quality figure should be presented. The data used in this exercise is publicly available data from Spotify of over 30,000 different songs classified by artist, genre, and several other factors.

## Load Libraries

```{r}
library(here)
library(tidyverse)
library(tidytuesdayR) #Great source of free data, even outside of Tidy Tuesday submissions
```

## Load in Data

```{r}
spotify_songs <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-01-21/spotify_songs.csv')

view(spotify_songs)
```

## "Bad" Plot

```{r}

Bad_Plot_Spotify <- spotify_songs %>% 
  filter(track_artist %in% c("Tones and I", "Arizona Zervas", "KAROL G", "Maroon 5", "The Weeknd", "Post Malone")) %>% 
  ggplot(aes(x=track_artist))+
  geom_bar()+
  labs(title = "we the best music",
       y="")

Bad_Plot_Spotify
```

## "Good" Plot

```{r}
Good_Plot_Spotify <- spotify_songs %>% 
  filter(track_popularity %in% c(100,99,98,97,96,95)) %>% 
  ggplot(aes(y=track_artist, fill=playlist_genre))+
  geom_bar()+
   labs(title = "Artists of the Top Tracks of 2020",
        subtitle = "Separated by Genre",
        x="Count",
        y="Artist",
        fill = "Genre")+
  scale_color_viridis_d()

Good_Plot_Spotify

```
 
 