---
title: "Iterative Coding Lab"
author: "Evan Rank"
date: "4/26/2021"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)
```

## Introduction

  Today's goal is to calculate the mean and standard deviation of both temperature and light intensity of four separate tide pool data files, bringing the results into one dataframe using iterative coding methods; a for loop and mapping function will be showcased separately.

## Load Libraries

```{r}
library(tidyverse)
library(here)
library(purrr)
```

## For Loop method

# Bring in data using directory path

```{r}
tppath<-here("Week_13", "Data", "homework")

files <- dir(path = tppath, pattern = ".csv")#picks up all csv in the directory
files
```

# Assign new data frame

```{r}
tp_data<-data.frame(matrix(nrow = length(files), ncol = 5)) #mean and sd 2x2 columns, then one for pool name
colnames(tp_data)<-c("filename","mean_temp", "sd_temp", "mean_light_intensity", "sd_light_intensity")
tp_data
```

# Fill new data frame

```{r}
for (i in 1:length(files)){ # loop over the number of files 
  raw_data<-read_csv(paste0(tppath,"/",files[i])) 

   tp_data$filename[i]<-files[i]
 tp_data$mean_temp[i]<-mean(raw_data$Temp.C, na.rm =TRUE)
   tp_data$sd_temp[i]<-sd(raw_data$Temp.C, na.rm =TRUE)
  tp_data$mean_light_intensity[i]<-mean(raw_data$Intensity.lux, na.rm = TRUE)
  tp_data$sd_light_intensity[i]<-sd(raw_data$Intensity.lux, na.rm =TRUE)
}

tp_data
```

## Purrr Method

# Load in data

```{r}
tppath2<-here("Week_13", "Data", "homework") #same path
files2 <- dir(path = tppath2,pattern = ".csv",full.names = TRUE) #add full.names for function to read file and not just name
files2
```

# Mapping and calculating

```{r}
tpdata2<-files2 %>%
  set_names()%>%
  map_df(read_csv,.id = "filename") %>%
  group_by(filename) %>%
  summarise(mean_temp = mean(Temp.C, na.rm = TRUE),
            sd_temp = sd(Temp.C, na.rm = TRUE),
            mean_light_intensity = mean(Intensity.lux, na.rm = TRUE),
            sd_light_intensity = sd(Intensity.lux, na.rm = TRUE))

tpdata2
```

